Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-03 manuscripts/manuscript.Rmd
edits to Fig4, working on code for table 1

```{r reductions}
reduction_table <- sapply(c("0.10" = 0.10, "0.20" = 0.20, "0.30" = 0.30), function(reduction){
index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples })
write.csv(reduction_table, "../data/reduction_table.csv")
````

@@

```{r helper_fn_2} 
# Helper functions to extract the summary stats in different variables
stats_harvest <- function(dt){
v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}

stats_fishstock <- function(dt){
v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}
```

```{r helper_fn_3}
#' a simple function for reorganizing the data over the different "faction-lost" levels
get_trends <- function(tmp2){
  out <- melt(tmp2, id=c("reps", "var", "acor"))
  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
  out <- data.table(out)
  Ev = out[,mean(var),by=c('penalty', 'fraction')]
  SDv = out[,sd(var),by=c('penalty', 'fraction')]
  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
  harvest_trends <- data.table(penalty = Ev$penalty, 
                               fraction = Ev$fraction, 
                               Ev = Ev$V1, Ea = Ea$V1, 
                               SDv=SDv$V1, SDa = SDa$V1)
}
```

```{r Figure4_harvest}
sims_at_each_apple <- lapply(frac_lost, fig4)
harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
harvest_trends <- get_trends(harvest_stats)
```

```{r fishstock_trends}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)
```

@@

The comparisons shown in Figure 2 are for one realization (i.e. a
particular sequence of random number draws representing environmental
variability) and are made for a particular magnitude of policy
adjustment costs equal to `r reduction`% of the maximum expected net present value 
in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
how optimal harvest levels and corresponding optimal stock sizes are
affected by the magnitude of the costs of policy adjustment. This time
we show summary statistics across 50 replicate sets of environmental
conditions. We show the impact of policy adjustment costs on the
variance of both harvests and stock sizes through time; on the
autocorrelation of harvests and stock sizes through time; and on the
cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not?-->

@@

Interestingly, as suggested by the realization in Fig. 3, including a
fixed cost of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect. Follow-on
consequences for the other statistics are not as clear in this case.

@@

Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work.
-->

```{r Figure_4, fig.cap="(a) Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. (b) Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + 
  xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()

multiplot(Fig4a, Fig4b, cols=2)
```

```{r Figure_5, fig.cap = "(a) Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. (b) Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
Fig5a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()

Fig5b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()

multiplot(Fig5a, Fig5b, cols=2)

@@

>>>>

```{r reductions}
reduction_table <- sapply(c("0.10" = 0.10, "0.20" = 0.20, "0.30" = 0.30), function(reduction){
index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples })
write.csv(reduction_table, "components/data/reduction_table.csv")
````

@@

```{r fig4-stats}
summary_stats <- function(dt){
 harvest_var <- dt[,var(harvest), by=c("penalty_fn", "reps")]$V1
 harvest_acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 stock_var <- dt[,var(fishstock), by=c("penalty_fn", "reps")]$V1
 stock_acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 xcor <- dt[, ccf(fishstock, harvest, plot=FALSE)$acf[2], by=c("penalty_fn", "reps")]
 setnames(xcor, "V1", "cross-correlation")

 df <- data.frame('stock.variance' = stock_var, 
                  'stock.autocorrelation' = stock_acor, 
                  'harvest.variance' = harvest_var, 
                  'harvest.autocorrelation' = harvest_acor, 
                  xcor)

 # long format
 melt(df, id=c("penalty_fn", "reps"))
 }
```

```{r summary-stat-calc}
stats_summaries <- lapply(sims_at_each_apple, summary_stats)
# reformat list of data-frames as data frame with apple coef as a factor
stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
stats_df$L1 <- frac_lost[stats_df$L1]
names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
```

```{r split-factors}
# make statistic and timeseries separate factors
figure4_df <- stats_df
figure4_df$statistic <- figure4_df$variable
figure4_df$timeseries <- figure4_df$variable
stat_map <- c(harvest.variance = 'variance', stock.variance='variance', stock.autocorrelation='autocor',harvest.autocorrelation='autocor', cross.correlation='cross.correlation')
series_map <- c(harvest.variance = 'harvest', stock.variance='stock', stock.autocorrelation='stock',harvest.autocorrelation='harvest', cross.correlation='both')

figure4_df$statistic <- stat_map[figure4_df$statistic]
figure4_df$timeseries <- series_map[figure4_df$timeseries]
```

```{r table-calc}
source("componetns/compute_error_table.R")
sigmas <- c(0.01, 0.1, 0.2)
reductions <- 1:3
out <- lapply(sigmas, function(s){
  lapply(reductions, function(r){
    compute_error_table(r = r, sigma = s)    
  })
})

who <- names(out[[1]][[1]])
error_df <- melt(out, id=who)              
```

```{r clean-table}
df <- error_df[2:8]
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
df2 <- melt(df, id=who)
who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
df3 <- melt(df2, id=who)
names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
df3$reduction <- as.factor(df3$reduction)

#ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
```

@@

The comparisons shown in Figure 2 are for one realization (i.e. a
particular sequence of random number draws representing environmental
variability) and are made for a particular magnitude of policy
adjustment costs equal to `r reduction`% of the maximum expected net present value 
in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
how optimal harvest levels and corresponding optimal stock sizes are
affected by the magnitude of the costs of policy adjustment. This time
we show summary statistics across 50 replicate sets of environmental
conditions. We show the impact of policy adjustment costs on the
variance of both harvests and stock sizes through time; on the
autocorrelation of harvests and stock sizes through time; and on the
cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->

@@

Interestingly, as suggested by the realization in Fig. 2, including a
fixed cost of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect. Follow-on
consequences for the other statistics are not as clear in this case.

@@

Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work. - Paul
-->
<!--
Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB
-->

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}

with_xcor_plot <- 
ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  facet_wrap(~variable, scales = "free_y") +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line")
with_xcor_plot

ggplot(subset(figure4_df, statistic != "cross.correlation"), aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_grid(statistic ~ timeseries, scale="free") + theme_bw()

@@

```{r Table1, results="asis", echo=FALSE}
df4 <- error_df[c(1,2,4,6,7)]
plyr::arrange(df4, penalty_fn)
pandoc.table(df4)
```
